### 2020-08-12 reports/article.tex
boo

\subsection*{Relationships between the spatial pattern of tree canopy on urban heat mitigation}

@@

\begin{table}[!h]
  % \begin{adjustwidth}{-.4\textwidth}{0cm} % Comment out/remove adjustwidth environment if table fits in text column.
  \footnotesize % Font size can be changed to match table content. Recommend 10 pt.
  \renewcommand{\arraystretch}{1.5} % vertical spacing
  \centering
  \begin{tabular}{p{.16\textwidth} p{.28\textwidth} p{.46\textwidth}} 
    \toprule
    \textbf{Category} & \textbf{Metric name} & \textbf{Description} \\
    \midrule
    Composition & Percentage of landscape (PLAND) & Percentage of landscape, in terms of area, occupied by pixels with high tree canopy cover \\
    Configuration & Mean patch size (MPS) & Average size (in hectares) of the patches formed by pixels with high tree canopy cover \\
    & Edge density (ED) & Sum of the lengths of all edge segments between pixels with high tree canopy cover an other pixels, per area unit (in m/hectare) \\
    & Mean shape index (MSI) & Average shape index of the patches formed by pixels with high tree canopy cover \\
    \bottomrule  
  \end{tabular}
  \caption{\label{tab:selected-metrics}Selected landscape metrics. A more thorough description can be found in the documentation of the software FRAGSTATS v4 \cite{mcgarigal2012fragstats}}
  % \end{adjustwidth}
\end{table}

@@

\subsection*{Relationship between }

>>>>

\subsection*{Relationship between the spatial pattern of tree canopy on urban heat mitigation}

@@

\begin{table}[!h]
  % \begin{adjustwidth}{-.4\textwidth}{0cm} % Comment out/remove adjustwidth environment if table fits in text column.
  \footnotesize % Font size can be changed to match table content. Recommend 10 pt.
  \renewcommand{\arraystretch}{1.5} % vertical spacing
  \centering
  \begin{tabular}{p{.16\textwidth} p{.28\textwidth} p{.46\textwidth}} 
    \toprule
    \textbf{Category} & \textbf{Metric name} & \textbf{Description} \\
    \midrule
    Composition & Percentage of landscape (PLAND) & Percentage of landscape, in terms of area, occupied by pixels with high tree canopy cover \\
    Configuration & Mean patch area (AREA\_MN) & Average size (in hectares) of the patches formed by pixels with high tree canopy cover \\
    & Mean shape index (SHAPE\_MN) & Average shape index of the patches formed by pixels with high tree canopy cover \\
    & Edge density (ED) & Sum of the lengths of all edge segments between pixels with high tree canopy cover an other pixels, per area unit (in m/hectare) \\    
    \bottomrule  
  \end{tabular}
  \caption{\label{tab:selected-metrics}Selected landscape metrics. A more thorough description can be found in the documentation of the software FRAGSTATS v4 \cite{mcgarigal2012fragstats}}
  % \end{adjustwidth}
\end{table}

@@

\subsection*{Relationship between the spatial pattern of tree canopy on urban heat mitigation}

\begin{table}[H]
  \begin{center}
    \begin{tabular}{ p{.1\textwidth} p{.14\textwidth} p{.14\textwidth} p{.14\textwidth} p{.14\textwidth} p{.14\textwidth} }
      \toprule
      Scale & PLAND & AREA\_MN & SHAPE\_MN & ED & DIST \\
      \midrule
      600~m & -0.0036551** & 0.0338958 & -0.1508861** & 0.0003209* & -0.0001311** \\
       & -0.4126989** & -0.113218* & -0.160736** & 0.3619957** & -0.5551176** \\      
      \bottomrule
    \end{tabular}
    \caption{\label{tab:spatial-regression} Correlation coefficients between the air temperature and the features of the spatial regression. }

  \end{center}
\end{table}

% ALSO:
% - metrics to show that spatial regression is needed (spatial autocorrelation)
% - heteroscedasticity
